Title

### 2017-04-10 cthpc-2017/puyuma.tex
Correct the spelling and add the \FloatBarrier in Latex.

\documentclass[conference]{IEEEtran}
\usepackage[english]{babel}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{url,hyperref,graphicx,float,times}
\usepackage{textcomp}
\usepackage{cite}
\usepackage[caption=false,font=footnotesize]{subfig}

@@

@@

Robot Operating System, or ROS, is a system designed for robot. Instead a operating system, it’s a framework above operating system, proposing a identical interface around different machine architecture. As a middleware for interprocess communication, ROS takes a publish–subscribe pattern for data transfer abstraction. The implementation support multiple programming language API, enhance the system flexibility and scalability.

@@

Real-time operating system (RTOS) guarantees the response time of real time task within specified time constraints, often referred to as “deadline”. A soft real-time OS can usually or generally meet a deadline, and a hard real-time OS can always meet a deadline deterministically. The real-time Linux extension for this project is Xenomai which provides two mechanisms, Cobalt and Mercury, to implement the real-time task. This paper just mention the Cobalt mechanism which we used for the autonomous vehicle system. Xenomai built the small extension named Cobalt into the Linux kernel,shown in figure \ref{fig:xeno_arch}, dealing with all time-critical activities, such as handling interrupts, and scheduling real-time threads. The Cobalt core has higher priority over the native Linux kernel. With the Cobalt mechanism, this project benefits from the RTOS API provided by Xenomai and abundant Linux services provided by native Linux kernel. As the above, this project also gains the portability since the real time environment based on Linux.

\begin{figure}
\centering
\includegraphics[width=3in]{img/arch.png}
\caption{System Architecture}
\label{fig:overall_arch}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=3in]{img/xeno_arch.png}
\caption{Xenomai Cobalt Architecture}
\label{fig:xeno_arch}
\end{figure}

@@

\begin{table}
\centering
\caption{Hardware List}
\label{hardware_list}
\begin{tabular}{ll}
Hardware                & Budgets  \\
Raspberry Pi3 Model B   & 1600 NTD \\
Raspberry Pi camera     & 698 NTD  \\
2S LiPo battery 1300mAh & 240 NTD  \\
Sandisk 16G microSD     & 185 NTD  \\
L298N motor driver      & 263 NTD  \\
Car frame               & 375 NTD  \\
DC voltage regulator    & 105 NTD  \\
Total                   & 3466 NTD
\end{tabular}
\end{table}

@@

The Linux kernel is resident in memory after the booting stage, therefore the large kernel image and kernel module size may increase cache miss probability. In order to minimize the latency effect from Linux kernel, we remove the unnecessary kernel module and file system to reduce the kernel module size. In addition, we adjust the performance related kernel configuration to ease the burden of interrupt handling.

@@

The Linux kernel is resident in memory after the booting stage, therefore the large kernel image and kernel module size may increase cache miss probability. In order to minimize the latency effect from Linux kernel, we remove the unnecessary kernel module and file system to reduce the kernel module size. In addition, we adjust the performance related kernel configuration to ease the burden of interrupt handling.

@@

Camera calibration is a early stage mission before doing the computer vision. There are two set of parameters need to be found, intrinsic parameters and extrinsic parameter. By estimate them we can know the relation between 2D image plane and 3D world.

@@

\begin{figure}
\centering
\includegraphics[width=2in]{img/extrinsic.png}
\caption{Ground Projection}
\label{fig:extrinsic}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=2in]{img/lane_detect.png}
\caption{Segments visualization}
\label{fig:lane_detect}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=3.5in]{img/controller.png}
\caption{Control Diagram}
\label{fig:controller}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=2in]{img/stock_kernel.png}
\caption{Stock Kernel Performance}
\label{fig:stock_kernel_perf}
\end{figure}

@@

>>>>

\documentclass[conference]{IEEEtran}
\usepackage[english]{babel}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{url,hyperref,graphicx,float,times}
\usepackage{textcomp}
\usepackage{cite}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{placeins}
%\usepackage{flafter}

@@

\FloatBarrier
\begin{figure}
	\centering
	\includegraphics[width=3in]{img/arch.png}
	\caption{System Architecture}
	\label{fig:overall_arch}
\end{figure}

@@

Robot Operating System, or ROS, is a system designed for robot. Instead a operating system, it’s a framework above operating system, proposing a identical interface around different machine architecture. As a middleware for interprocess communication, ROS takes a publish-subscribe pattern for data transfer abstraction. The implementation support multiple programming language API, enhance the system flexibility and scalability.

@@

Real-time operating system (RTOS) guarantees the response time of real time task within specified time constraints, often referred to as “deadline”. A soft real-time OS can usually or generally meet a deadline, and a hard real-time OS can always meet a deadline deterministically. The real-time Linux extension for this project is Xenomai which provides two mechanisms, Cobalt and Mercury, to implement the real-time task. This paper just mention the Cobalt mechanism which we used for the autonomous vehicle system. Xenomai built the small extension named Cobalt into the Linux kernel,shown in figure \ref{fig:xeno_arch}, dealing with all time-critical activities, such as handling interrupts, and scheduling real-time threads. The Cobalt core has higher priority over the native Linux kernel. With the Cobalt mechanism, this project benefits from the RTOS API provided by Xenomai and abundant Linux services provided by native Linux kernel. As the above, this project also gains the portability since the real time environment is based on Linux.

\begin{figure}
	\centering
	\includegraphics[width=3in]{img/xeno_arch.png}
	\caption{Xenomai Cobalt Architecture}
	\label{fig:xeno_arch}
\end{figure}
\FloatBarrier

@@

\begin{table}
	\centering
	\caption{Hardware List}
	\label{hardware_list}
	\begin{tabular}{ll}
		Hardware                & Budgets  \\
		Raspberry Pi3 Model B   & 1600 NTD \\
		Raspberry Pi camera     & 698 NTD  \\
		2S LiPo battery 1300mAh & 240 NTD  \\
		Sandisk 16G microSD     & 185 NTD  \\
		L298N motor driver      & 263 NTD  \\
		Car frame               & 375 NTD  \\
		DC voltage regulator    & 105 NTD  \\
		Total                   & 3466 NTD
	\end{tabular}
\end{table}
\FloatBarrier

@@

The Linux kernel is resident in memory after the booting stage, therefore the large kernel image and kernel module size may increase probability of cache miss. In order to minimize the latency effect from Linux kernel, we remove the unnecessary kernel module and file system to reduce the kernel module size. In addition, we adjust the performance related kernel configuration to ease the burden of interrupt handling.

@@

Most system use pulse width modulation (PWM) to simulate the analog signal for smooth motor controlling. PWM signal was often generated by hardware, known as hardware PWM. On the contrary, using general-purpose input/output (GPIO) to simulate the PWM signal, known as software PWM.

We built the software PWM kernel module with Xenomai real-time API, we named it KsoftPWM, for this project. With the real-time application, it ensures the precision of KsoftPWM signal generation. Furthermore, the KsoftPWM was built in kernel space to eliminate the system call overhead from user space.

@@

Camera calibration is an early stage mission before doing the computer vision. There are two set of parameters need to be found, intrinsic parameters and extrinsic parameter. By estimate them we can know the relation between 2D image plane and 3D world.

@@

\begin{figure}	
	\centering
	\includegraphics[width=2in]{img/extrinsic.png}
	\caption{Ground Projection}
	\label{fig:extrinsic}
\end{figure}
\FloatBarrier

@@

\FloatBarrier
\begin{figure}
	\centering
	\includegraphics[width=2in]{img/lane_detect.png}
	\caption{Segments visualization}
	\label{fig:lane_detect}
\end{figure}

@@

\FloatBarrier
\begin{figure}	
	\centering
	\includegraphics[width=3.5in]{img/controller.png}
	\caption{Control Diagram}
	\label{fig:controller}
\end{figure}

@@

\FloatBarrier
\begin{figure}	
	\centering
	\includegraphics[width=2in]{img/stock_kernel.png}
	\caption{Stock Kernel Performance}
	\label{fig:stock_kernel_perf}
\end{figure}

@@

\FloatBarrier
